
\documentclass[10pt,-letter paper]{article}
\usepackage[left=1in, right=0.75in, top=1in, bottom=0.75in]{geometry}
\usepackage{graphicx} % Required for inserting images
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
  frame=single,
    breaklines=true
    }
    \let\vec\mathbf{}
    \usepackage{enumitem}
    \usepackage{graphicx}
    \usepackage{siunitx}
    \let\vec\mathbf{}
    \usepackage{enumitem}
    \usepackage{graphicx}
    \usepackage{enumitem}
    \usepackage{tfrupee}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{mwe} % for blindtext and example-image-a in example
    \usepackage{wrapfig}
    \graphicspath{{figs/}}
    \providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
    \providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
    \newcommand{\sgn}{\mathop{\mathrm{sgn}}}
    \providecommand{\abs}[1]{\left\vert#1\right\vert}
    \providecommand{\res}[1]{\Res\displaylimits_{#1}} 
    
    \providecommand{\norm}[1]{\left\lVert#1\right\rVert}
    %\providecommand{\norm}[1]{\lVert#1\rVert}
    \providecommand{\mtx}[1]{\mathbf{#1}}
    \providecommand{\mean}[1]{E\left[ #1 \right]}
    \providecommand{\fourier}{\overset{\mathcal{F}}{ \rightleftharpoons}}
    %\providecommand{\hilbert}{\overset{\mathcal{H}}{ \rightleftharpoons}}
    \providecommand{\system}{\overset{\mathcal{H}}{ \longleftrightarrow}}
     %\newcommand{\solution}[2]{\textbf{Solution:}{#1}}
     %\newcommand{\solution}{\noindent \textbf{Solution: }}
     \newcommand{\cosec}{\,\text{cosec}\,}
     \providecommand{\dec}[2]{\ensuremath{\overset{#1}{\underset{#2}{\gtrless}}}}
     \newcommand{\myvec}[1]{\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}
     \newcommand{\myaugvec}[2]{\ensuremath{\begin{amatrix}{#1}#2\end{amatrix}}}
     \newcommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
     \title{MATHEMATICS}
     \author{SECTION A}
     \date{\today}
     \begin{document}

     \maketitle

     \begin{enumerate}
     \item If $A$ is a square matrix of order $2$ and $\mydet{A}$ = $4$,then find the value of $\mydet{2\cdot AA'}$, where $A'$ is the transpose of matrix $A$.

\item Find the angle between the line $\overrightarrow{r}=\brak{2\hat{i}-\hat
{j}+3\hat{k}}+\lambda\brak{3\hat{i}-\hat{j}+2\hat{k}}$ and the plane $\overrightarrow{r}.\brak{\hat{i}+\hat{j}+\hat{k}}=3$.

\item Find the co-ordinates of the point,where the line $\frac{x+2}{1}=\frac{y-5}{3}=\frac{z+1}{5}$ cuts the yz-plane.

\item Find the differential equation representing the family of curves $y=-Acos 3x+B sin 3x$.

\item Find the differential of the function $\cos^{-1}\brak{\sin 2x}$ w.r.t.$x$.

\item If an operation $\ast$ on the set of integers Z is defined by $a \ast b = 2a^{2}+b$, then find 
\begin{enumerate}
	\item whether it is a binary or not, and
	\item if a binary, then is it commutative or not. 
\end{enumerate}

\item Four cards are drawn one by one with replacement from a well-shuffled deck of playing cards. Find the probability that at least three cards are of diamonds.

\item The probability of two students $A$ and $B$ coming to school on time are $\frac{2}{7}$ and $\frac{4}{7}$,respectively. Assuming that the events '$A$ coming on time' and '$B$ coming on time' are independent, find the probability of only one of them coming to school on time.

\item Find the value of $\brak{x-y}$ from the matrix equation
	$2\myvec{x & 5 \\ 7 & y-3} + \myvec{-3 & -4 \\ 1 & 2}= \myvec{7 & 6 \\ 15 & 14}$

\item Solve the following differential equation :
\begin{align*}          
	 \brak{y + 3x^{2}}\frac{dx}{dy}=x
\end{align*}

\item Using vectors, prove that the points $\brak{2,-1,3},\brak{3,-5,1}$ and 
	$\brak{-1,11,9}$ are collinear.

\item For any two vectors $\overrightarrow{a}$ and $\overrightarrow{b}$, prove that 
\begin{align*}
\brak{{\overrightarrow{a} \times \overrightarrow{b}}}^2 = \overrightarrow{a}^2  \overrightarrow{b}^2 - \brak{{\overrightarrow{a} \cdot \overrightarrow{b}}}^2
\end{align*}
\item Find:\begin{align*}
		\int\frac{x-1}{\brak{x-2}\brak{x-3}}dx
\end{align*}
\item Integrate:

	\begin{align*}
		\frac{e^x}{\sqrt{5-4e^x-e^{2x}}}
	\end{align*}
		     with respect to x.

\item Find:
	\begin{align*}
		\int {e^x\brak{\frac{2+\sin 2x}{2 \cos^2 x}}} dx
	\end{align*}

\item If $A$ and $B$ are independent events with $P\brak{A}=\frac{3}{7}$ and $P\brak{B}=\frac{2}{5}$, then find $P\brak{A'\bigcap B'}$.

\item Find the equation of the plane passing through $\brak{-1,3,2}$ and perpendicular to the planes $x+2y+3z=5$ and $3x+3y+z=0$.

\item Evaluate: 
	\begin{align*}
		\int_{1}^{5} \brak{\vert{x-1}\vert+\vert{x-2}\vert+\vert{x-4}\vert} dx
	\end{align*}

\item If $x$, $y$, $z$ are different and $\Delta=\mydet{x & x^2 & x^3 -1\\y & y^2 & y^3 -1\\z & z^2 & z^3 -1} = 0$ ,then using properties of determinants, show that $xyz$ = 1.
\item Prove that : 
	\begin{align*}
		\sin^{-1}\frac{4}{5}+\tan^{-1}\frac{5}{12}+\cos^{-1}\frac{63}{65}=\frac{\pi}{2}
	\end{align*}

\item Using vectors, find the value of $x$ such that the four points A$\brak{x,5,-1}$,B$\brak{3,2,1}$,C$\brak{4,5,5}$ and D$\brak{4,2,-2}$ are coplanar.

\item Differentiate $\tan^{-1}\frac{3x-{x^3}}{1-3x^2},\vert{x}\vert<\frac{1}{\sqrt{3}}$ w.r.t. $\tan^{-1}\frac{x}{\sqrt{1-x^2}}$.

\item If $\sqrt{1-x^2}+\sqrt{1-y^2}=a\brak{x-y},\vert{x}\vert<1,\vert{y}\vert<1$, show that $\frac{dy}{dx}=\sqrt{\frac{1-y^2}{1-x^2}}$.

\item Prove that the relation $\mathbf{R}$ in the set $A = \cbrak{1,2,3,4,5,6,7}$ given by $\mathbf{R}=\cbrak{\brak{a,b}:\mydet{a-b}\text{is even}}$ is an equivalence relation.

\item Show that the function $f$ in $A = R-\{\frac{2}{3}\}$ defined as $f\brak{x} = \frac{4x+3}{6x-4}$ is one-one and onto. Hence, find $f^{-1}$.

\item Find the particular solution of the differential equation: $\brak{1+e^{2x}}{dy}+\brak{1+y^2}{e^{x}dx}=0$, given that $y\brak0=1$.

\item Find the particular solution of the differential equation: $x\frac{dy}{dx}\sin\brak{\frac{y}{x}}+x-y\sin\brak{\frac{y}{x}}=0$,given that $y\brak1=\frac{\pi}{2}$.

\item If $y = \brak{\sin{x}^x}+\sin^{-1}\brak{\sqrt{1-x^2}}$, then find $\frac{dy}{dx}$

\item Find:
	\begin{align*}
		\int\cos{2x}\cos{4x}\cos{6x}~dx
	\end{align*}

\item Find the interval in which the function $f$ given by $f\brak{x}=\sin2x+\cos2x,0\leq{x}\leq{\pi}$ is strictly decreasing.

\item Using elementary row transformations,find the inverse of the matrix $\myvec{3 & 0 & -1\\
	2 & 3 & 0\\
	0 & 4 & 1\\}$.

\item Using matrices, solve the following system of linear equations:
	\begin{align*}
		2x+3y+10z=4\\
		4x-6y+5z=1\\
		6x+9y-20z=2
	\end{align*}

\item Using integration, find the area of the following region :
	\begin{align*}
	\{\brak{x,y}:x^2+y^2\leq16a^2~and~y^2\leq6ax\}
	\end{align*}

	\item Using integration, find the area of triangle $ABC$ bounded by the lines 
		\begin{align*}
		4x-y+5=0, x+y-5=0~and~x-4y+5=0.
		\end{align*}

		\item A company manufactures two types of novelty souvenirs made of plywood. Souvenirs of type $A$ require $5$ minutes each for cutting and $10$ minutes each for assembling. Souvenirs of type $B$ require $8$ minutes each for cutting and $8$ minutes each for assembling. There are $3$ hours $20$ minutes available for cutting and $4$ hours for assembling. The profit for type $A$ souvenirs is \rupee~$100$ each and for type $B$ souvenirs, profit is \rupee~$120$ each. How many souvenirs of each type should the company manufacture in order to maximise the profit ? Formulate the problem as a LPP and then solve it graphically.

		\item Find the vector equation of the line passing through$\brak{2,1,-1}$ and parallel to the line $\overrightarrow{r}=\brak{\hat{i}+\hat{j}}+\lambda\brak{2\hat{i}-\hat{j}+\hat{k}}$.Also, find the distance between these two lines.


		\item Find the coordinates of the foot $Q$ of the perpendicular drawn from the point $P\brak{1,3,4}$ to the plane $2x-y+z+3=0$. Find the distance $PQ$ and the image of $P$ treating the planes as a mirror.

		\item A card from a pack of $52$ playing cards is lost. From the remaining cards of the pack, two cards are drawn at random (without replacement) and both are found to be spades. Find the probability of the lost card being a spade.

		\item Prove that the radius of the right circular cylinder of greatest curved surface area which can be inscribed in a given cone is half of that of the cone.
		
\end{enumerate}
     \end{document}
